### 2021-04-25 paper/output/document/futurework.tex
prof amin's feedback

This final question is both technical and philosophical, and will be interesting to explore in the written
component of my thesis. This question is related to Kant's distinction between analytic and synthetic reasoning \cite{groundwork}. 
Analytic statements are true simply by virtue of their meaning, such as ``All bachelors are unmarried." Synthetic 
reasoning involves some contribution by the reasoner, in the form of new insight or facts about the world. 
Kant believes that ethics is synthetic a priori reasoning, but it is unclear if automated theorem provers 
like Isabelle are capable of anything more than analytic reasoning. Many of the basic proof solving 
tools like \texttt{simp} or \texttt{blast} simply unfold definitions and apply axioms, and they appear to 
perform analytic reasoning. smt solvers like \texttt{Nitpick} and \texttt{z3} (bundled with Isabelle) are 
candidates for synthetic reasoning.

Lastly, I hope to explore Kant's argument that the three formulations of the categorical imperative are 
equivalent. This hypothesis has been the subject of controversy, but many neo-Kantians believe that his 
claim is plausible, if not true. Armed with formalizations of each formulation, I will have all the tools 
necessary to test this hypothesis. I would like to either prove or disprove this hypothesis
for my formalization, and analyze the philosophical implications of my result.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/futurework.thy%:%
%:%24=7%:%
%:%36=9%:%
%:%37=10%:%
%:%38=11%:%
%:%39=12%:%
%:%40=13%:%
%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%44=17%:%
%:%45=18%:%
%:%46=19%:%
%:%47=20%:%
%:%48=21%:%
%:%49=22%:%
%:%50=23%:%
%:%51=24%:%
%:%52=25%:%
%:%53=26%:%
%:%54=27%:%
%:%55=28%:%
%:%56=29%:%
%:%57=30%:%
%:%58=31%:%
%:%59=32%:%
%:%60=33%:%
%:%61=34%:%
%:%62=35%:%
%:%63=36%:%
%:%64=37%:%
%:%65=38%:%
%:%66=39%:%
%:%67=40%:%
%:%68=41%:%
%:%69=42%:%
%:%70=43%:%
%:%71=44%:%
%:%72=45%:%

>>>>

This final question is both technical and philosophical, and will be interesting to explore in the written
component of my thesis. This question is related to Kant's distinction between analytic and synthetic reasoning \cite{groundwork}. 
Analytic statements are true simply by virtue of their meaning, such as ``All bachelors are unmarried." Synthetic 
reasoning involves some contribution by the reasoner, in the form of new insight or facts about the world.
Kant presents the statements ``All bachelors are alone" and ``7+5=12" as examples of synthetic propositions. 
The analytic/synthetic distinction is hotly debated and has been refined significantly since Kant, and this 
area will require further research.

Kant believes that ethics is synthetic a priori reasoning, but it is unclear if automated theorem provers 
like Isabelle are capable of anything more than analytic reasoning. Many of the basic proof solving 
tools like \texttt{simp} or \texttt{blast} simply unfold definitions and apply axioms, and they appear to 
perform analytic reasoning. SMT solvers like \texttt{Nitpick} and \texttt{z3} (bundled with Isabelle) are 
candidates for synthetic reasoning. Model finding seems more sophisticated than the simple unfolding
of definitions, but this requires further exploration.

Lastly, I hope to explore Kant's argument that the three formulations of the categorical imperative are 
equivalent. This hypothesis has been the subject of controversy, but many neo-Kantians believe that his 
claim is plausible, if not true. Armed with formalizations of each formulation, I will have all the tools 
necessary to test this hypothesis. I would like to either prove or disprove this hypothesis
for my formalization, and analyze the philosophical implications of my result.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/futurework.thy%:%
%:%24=7%:%
%:%36=9%:%
%:%37=10%:%
%:%38=11%:%
%:%39=12%:%
%:%40=13%:%
%:%41=14%:%
%:%42=15%:%
%:%43=16%:%
%:%44=17%:%
%:%45=18%:%
%:%46=19%:%
%:%47=20%:%
%:%48=21%:%
%:%49=22%:%
%:%50=23%:%
%:%51=24%:%
%:%52=25%:%
%:%53=26%:%
%:%54=27%:%
%:%55=28%:%
%:%56=29%:%
%:%57=30%:%
%:%58=31%:%
%:%59=32%:%
%:%60=33%:%
%:%61=34%:%
%:%62=35%:%
%:%63=36%:%
%:%64=37%:%
%:%65=38%:%
%:%66=39%:%
%:%67=40%:%
%:%68=41%:%
%:%69=42%:%
%:%70=43%:%
%:%71=44%:%
%:%72=45%:%
%:%73=46%:%
%:%74=47%:%
%:%75=48%:%
%:%76=49%:%
%:%77=50%:%

### 2021-04-25 paper/output/document/paper.tex
prof amin's feedback

 While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
including contrary-to-duty paradoxes \footnote{The paradigm case of a contrary-to-duty paradox is the 
Chisholm paradox. Consider the following statements: \begin{enumerate}
\item It ought to be that Tom ought helps his neighbors
\item It ought to be that if Tom goes to help his neighbors, he tells them he is coming
\item If Tom does not go to help his neighbors, he ought not tell them that he is coming
\item Tom does not help his neighbors
\end{enumerate} 
These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
contradiction results because the logic cannot handle violations of duty mixed with
conditionals. \cite{chisholm, ctd}
}. 
In situations where duty is violated, the logic breaks down 
and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Dyadic Deontic Logic%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \cite{CJDDL}. 
It introduces a dyadic obligation operator $O\{A \vert B\}$ 
to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1, neighborhood2}, instead of the Kripke semantics. 
Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
each world is mapped to the set of propositions obligated at that world, where a proposition $p$ is defined as 
the worlds at which the $p$ is true.

>>>>

 While SDL is appreciable for its simplicity, it suffers a variety of well-documented paradoxes, 
including contrary-to-duty paradoxes \footnote{The paradigm case of a contrary-to-duty paradox is the 
Chisholm paradox. Consider the following statements: \begin{enumerate}
\item It ought to be that Tom helps his neighbors
\item It ought to be that if Tom helps his neighbors, he tells them he is coming
\item If Tom does not help his neighbors, he ought not tell them that he is coming
\item Tom does not help his neighbors
\end{enumerate} 
These premises contradict themselves, because items (2)-(4) imply that Tom ought not help his neighbors. The 
contradiction results because the logic cannot handle violations of duty mixed with
conditionals. \cite{chisholm, ctd}
}. 
In situations where duty is violated, the logic breaks down 
and produces paradoxical results. Thus, I use an improved deontic logic instead of SDL for this work.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Dyadic Deontic Logic%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I use as my base logic Carmo and Jones's dyadic deontic logic, or DDL, which improves on SDL \cite{CJDDL}. 
It introduces a dyadic obligation operator $O\{A \vert B\}$ 
to represent the sentence ``A is obligated in the context B". This gracefully handles contrary-to-duty
conditionals. The obligation operator uses a neighborhood semantics \cite{neighborhood1, neighborhood2}, instead of the Kripke semantics. 
Carmo and Jones define a function $ob$ that maps from worlds to sets of sets of worlds. Intuitively, 
each world is mapped to the set of propositions obligated at that world, where a proposition $p$ is defined as 
the worlds at which the $p$ is true.

### 2021-04-25 paper/output/document/paper31.tex
prof amin's feedback

Let's now consider a naive reading of the Formula of Universal Law (FUL): 'act only in accordance 
with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
An immediate translation to DDL is that if A is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it.

@@

\ wrong{\isacharunderscore}if{\isacharunderscore}posibly{\isacharunderscore}wrong{\isacharcolon}\isanewline

@@

  Free variable:
    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ cw{\isacharparenright}\ {\isasymand}\ lie\ me\ cw}. The 
naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
handle this example appropriately.

@@

The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disupted, but the rough idea holds nonetheless. See \cite{kohl} for more.}

@@

logics evolved\cite{cresswell} specifically from this principle, so this should hold in both my 

@@

%:%309=171%:%
%:%310=172%:%
%:%311=173%:%
%:%312=174%:%
%:%313=175%:%
%:%314=176%:%
%:%315=177%:%
%:%316=178%:%
%:%318=180%:%
%:%319=180%:%
%:%320=181%:%
%:%321=182%:%
%:%322=183%:%
%:%323=183%:%

@@

%:%329=183%:%
%:%330=183%:%
%:%332=184%:%
%:%333=185%:%
%:%334=186%:%
%:%335=187%:%
%:%336=188%:%
%:%337=189%:%
%:%347=191%:%
%:%348=192%:%
%:%349=193%:%
%:%350=194%:%
%:%351=195%:%
%:%352=196%:%
%:%361=198%:%
%:%373=200%:%
%:%374=201%:%
%:%375=202%:%
%:%376=203%:%
%:%377=204%:%
%:%378=205%:%
%:%379=206%:%
%:%380=207%:%
%:%381=208%:%
%:%382=209%:%
%:%383=210%:%
%:%384=211%:%
%:%386=213%:%
%:%387=213%:%
%:%388=214%:%
%:%389=215%:%
%:%390=216%:%
%:%391=216%:%

@@

%:%397=216%:%
%:%398=216%:%
%:%400=217%:%
%:%401=218%:%
%:%402=219%:%
%:%403=220%:%
%:%404=220%:%
%:%406=221%:%
%:%407=222%:%
%:%408=222%:%
%:%410=223%:%

@@

%:%421=226%:%
%:%422=227%:%
%:%424=229%:%
%:%425=229%:%
%:%426=230%:%
%:%427=231%:%
%:%428=232%:%
%:%429=232%:%
%:%431=232%:%
%:%435=232%:%
%:%436=232%:%
%:%438=233%:%
%:%439=234%:%
%:%440=235%:%
%:%441=236%:%
%:%442=236%:%
%:%444=237%:%
%:%454=239%:%
%:%458=241%:%
%:%459=242%:%
%:%460=243%:%
%:%461=244%:%
%:%463=246%:%
%:%464=246%:%
%:%465=247%:%
%:%466=248%:%
%:%467=249%:%
%:%468=249%:%

@@

%:%474=249%:%
%:%475=249%:%
%:%477=250%:%
%:%478=251%:%
%:%479=252%:%
%:%480=253%:%
%:%481=253%:%
%:%483=254%:%
%:%493=256%:%
%:%494=257%:%
%:%495=258%:%
%:%497=260%:%
%:%498=260%:%
%:%499=261%:%
%:%500=262%:%
%:%501=263%:%
%:%502=263%:%

@@

%:%508=263%:%
%:%509=263%:%
%:%511=264%:%
%:%512=265%:%
%:%513=266%:%
%:%514=266%:%
%:%516=267%:%
%:%526=269%:%
%:%527=270%:%
%:%528=271%:%
%:%530=273%:%
%:%531=273%:%
%:%532=274%:%
%:%533=275%:%
%:%534=276%:%
%:%535=277%:%
%:%536=278%:%
%:%537=278%:%
%:%544=279%:%
%:%545=279%:%
%:%546=280%:%
%:%547=280%:%
%:%548=281%:%
%:%549=281%:%
%:%550=282%:%
%:%551=282%:%
%:%552=282%:%
%:%553=282%:%
%:%555=283%:%
%:%556=284%:%
%:%557=284%:%
%:%558=285%:%
%:%559=285%:%
%:%560=285%:%
%:%562=286%:%
%:%563=287%:%
%:%564=288%:%
%:%565=289%:%

@@

%:%567=290%:%
%:%569=291%:%
%:%579=293%:%
%:%580=294%:%
%:%581=295%:%
%:%582=296%:%
%:%583=297%:%
%:%585=299%:%
%:%586=299%:%
%:%587=300%:%
%:%588=301%:%
%:%589=302%:%
%:%590=302%:%

@@

%:%596=302%:%
%:%597=302%:%
%:%599=303%:%
%:%600=304%:%
%:%601=305%:%
%:%602=306%:%
%:%603=307%:%
%:%613=309%:%
%:%614=310%:%
%:%618=312%:%
%:%622=314%:%
%:%623=315%:%

@@

%:%626=318%:%
%:%627=318%:%
%:%628=319%:%
%:%631=320%:%
%:%635=320%:%
%:%636=320%:%
%:%638=321%:%
%:%639=321%:%
%:%641=322%:%
%:%642=323%:%
%:%643=324%:%
%:%644=325%:%
%:%645=326%:%
%:%655=328%:%
%:%656=329%:%
%:%657=330%:%
%:%658=331%:%
%:%660=333%:%
%:%661=333%:%
%:%662=334%:%
%:%665=335%:%
%:%669=335%:%
%:%670=335%:%
%:%671=335%:%
%:%673=336%:%
%:%674=336%:%

>>>>

Let's now consider a naive reading of the Formula of Universal Law (FUL): `act only in accordance 
with that maxim through which you can at the same time will that it become a universal law' \cite{groundwork}.
An immediate translation to DDL is that if A is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. Let's add this as an axiom to our logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Why add the categorical imperative as an axiom of this logic? The purpose of this logic is to 
perform ethical reasoning. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it.

@@

\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline

@@

  Free variable:
    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
}\isanewline
%
\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
the first line. It will then provide a model by specifying model components. For readability, all except for the 
free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
the opposite.%
}\isanewline
%
\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
the output.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ cw{\isacharparenright}\ {\isasymand}\ lie\ me\ cw}. The 
naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
handle this example appropriately.

@@

The ``ought implies can" principle is attributed to Kant\footnote{The exact philosophical credence of this view is disputed, but the rough idea holds nonetheless. See \cite{kohl} for more.}

@@

logics evolved \cite{cresswell} specifically from this principle, so this should hold in both my 

@@

%:%300=169%:%
%:%302=170%:%
%:%303=171%:%
%:%304=172%:%
%:%305=173%:%
%:%306=174%:%
%:%307=174%:%
%:%309=175%:%
%:%310=176%:%
%:%320=178%:%
%:%321=179%:%
%:%322=180%:%
%:%323=181%:%
%:%324=182%:%

@@

%:%326=184%:%
%:%327=185%:%
%:%329=187%:%
%:%330=187%:%
%:%331=188%:%
%:%332=189%:%
%:%333=190%:%
%:%334=190%:%
%:%336=190%:%
%:%340=190%:%
%:%341=190%:%
%:%343=191%:%
%:%344=192%:%
%:%345=193%:%
%:%346=194%:%
%:%347=195%:%
%:%348=196%:%
%:%358=198%:%
%:%359=199%:%
%:%360=200%:%
%:%361=201%:%
%:%362=202%:%
%:%363=203%:%
%:%372=205%:%
%:%384=207%:%
%:%385=208%:%
%:%386=209%:%
%:%387=210%:%
%:%388=211%:%
%:%389=212%:%
%:%390=213%:%
%:%391=214%:%
%:%392=215%:%

@@

%:%394=217%:%
%:%395=218%:%
%:%397=220%:%
%:%398=220%:%
%:%399=221%:%
%:%400=222%:%
%:%401=223%:%
%:%402=223%:%
%:%404=223%:%
%:%408=223%:%
%:%409=223%:%

@@

%:%412=225%:%
%:%413=226%:%
%:%414=227%:%
%:%415=227%:%
%:%417=228%:%
%:%418=229%:%
%:%419=229%:%
%:%421=230%:%
%:%422=231%:%
%:%432=233%:%
%:%433=234%:%
%:%435=236%:%
%:%436=236%:%
%:%437=237%:%
%:%438=238%:%
%:%439=239%:%
%:%440=239%:%
%:%442=239%:%
%:%446=239%:%
%:%447=239%:%
%:%449=240%:%
%:%450=241%:%
%:%451=242%:%
%:%452=243%:%
%:%453=243%:%
%:%455=244%:%
%:%465=246%:%
%:%469=248%:%

@@

%:%471=250%:%
%:%472=251%:%
%:%474=253%:%
%:%475=253%:%
%:%476=254%:%
%:%477=255%:%
%:%478=256%:%
%:%479=256%:%
%:%481=256%:%
%:%485=256%:%
%:%486=256%:%
%:%488=257%:%
%:%489=258%:%
%:%490=259%:%
%:%491=260%:%
%:%492=260%:%
%:%494=261%:%

@@

%:%505=264%:%
%:%506=265%:%
%:%508=267%:%
%:%509=267%:%
%:%510=268%:%
%:%511=269%:%
%:%512=270%:%
%:%513=270%:%
%:%515=270%:%
%:%519=270%:%
%:%520=270%:%
%:%522=271%:%
%:%523=272%:%
%:%524=273%:%
%:%525=273%:%
%:%527=274%:%
%:%537=276%:%
%:%538=277%:%
%:%539=278%:%
%:%541=280%:%
%:%542=280%:%
%:%543=281%:%
%:%544=282%:%
%:%545=283%:%
%:%546=284%:%
%:%547=285%:%
%:%548=285%:%
%:%555=286%:%
%:%556=286%:%
%:%557=287%:%
%:%558=287%:%
%:%559=288%:%
%:%560=288%:%
%:%561=289%:%
%:%562=289%:%
%:%563=289%:%
%:%564=289%:%

@@

%:%567=291%:%
%:%568=291%:%
%:%569=292%:%
%:%570=292%:%
%:%571=292%:%
%:%573=293%:%
%:%574=294%:%
%:%575=295%:%
%:%576=296%:%
%:%577=297%:%
%:%578=297%:%
%:%580=298%:%
%:%590=300%:%
%:%591=301%:%

@@

%:%593=303%:%
%:%594=304%:%
%:%596=306%:%
%:%597=306%:%
%:%598=307%:%
%:%599=308%:%
%:%600=309%:%
%:%601=309%:%
%:%603=309%:%
%:%607=309%:%
%:%608=309%:%
%:%610=310%:%
%:%611=311%:%
%:%612=312%:%
%:%613=313%:%
%:%614=314%:%

@@

%:%625=317%:%
%:%629=319%:%
%:%633=321%:%
%:%634=322%:%
%:%635=323%:%
%:%637=325%:%
%:%638=325%:%
%:%639=326%:%
%:%642=327%:%
%:%646=327%:%
%:%647=327%:%
%:%649=328%:%
%:%650=328%:%
%:%652=329%:%
%:%653=330%:%
%:%654=331%:%
%:%655=332%:%
%:%656=333%:%
%:%666=335%:%
%:%667=336%:%
%:%668=337%:%
%:%669=338%:%
%:%671=340%:%
%:%672=340%:%
%:%673=341%:%
%:%676=342%:%
%:%680=342%:%
%:%681=342%:%
%:%682=342%:%
%:%684=343%:%
%:%685=343%:%
